### 2019-12-01 Common/chapters/deep_learning.tex
Julien and Johan: make neural network with tikz

From a descriptive point of view, neural networks can simply be seen as a non linear applications that associate an input to an output with respect to certain parameters. The input can be images, sounds or whatever features that is numerical. The output of a neural network depends on the problem it tries to solve. In computer vision, the most common types of outputs  are classes (for classification problems) and pixel coordinates (for segmentation problems).\\
The figure \ref{neural_network} globally illustrates the concept of a neural network: in a fully connected neural network,  all inputs are given to all neurons of the first layer. Each neuron sums the incoming inputs, passes the result through a non linear function and sends it to all neuron of the next layer along an edge. Each edge between two neurons has a certain weight (a numerical value) that weights the importance of the output of the previous neuron.\\
From a mathematical point of view, a neural network can be defined as a non linear function $f$ that associates to an input $x$ an output $y$ with respect to parameters $\theta$.
\begin{equation}
y = f(x,\theta)
\end{equation}
The parameters $\theta$ are estimated from the training samples.
\begin{figure}[!h]
\centering
\includegraphics[width=1\textwidth, keepaspectratio=true]{./figures/neural_network.png}
\caption{Neural Network example}
\label{neural_network}
\end{figure}

>>>>

From a descriptive point of view, neural networks can simply be seen as a non linear applications that associate an input to an output with respect to certain parameters. The input can be images, sounds or whatever features that is numerical. The output of a neural network depends on the problem it tries to solve. In computer vision, the most common types of outputs  are classes (for classification problems) and pixel coordinates (for segmentation problems).\\
The figure \ref{neural_network} globally illustrates the concept of a neural network: in a fully connected neural network,  all inputs are given to all neurons of the first layer. Each neuron sums the incoming inputs, passes the result through a non linear function and sends it to all neuron of the next layer along an edge. Each edge between two neurons has a certain weight (a numerical value) that weights the importance of the output of the previous neuron.\\
From a mathematical point of view, a neural network can be defined as a non linear function $f$ that associates to an input $x$ an output $y$ with respect to parameters $\theta$.
\begin{equation}
y = f(x,\theta)
\end{equation}
The parameters $\theta$ are estimated from the training samples.
%\begin{figure}[!h]
%\centering
%\includegraphics[width=1\textwidth, keepaspectratio=true]{./figures/neural_network.png}
%\caption{Neural Network example}
%\label{neural_network}
%\end{figure}

\begin{figure}[!h]
\centering
	\begin{tikzpicture}[x=1.5cm, y=1.5cm, >=stealth]

	\foreach \m/\l [count=\y] in {1,2,3,4}
	  \node [every neuron/.try, neuron \m/.try] (input-\m) at (0,2.5-\y) {};

	\foreach \m [count=\y] in {1,2}
	  \node [every neuron/.try, neuron \m/.try ] (hidden-\m) at (2,2-\y*1.25) {};

	\foreach \m [count=\y] in {1}
	  \node [every neuron/.try, neuron \m/.try ] (output-\m) at (4,0.15) {};

	% input layer
	\foreach \l [count=\i] in {1,2,3,4}
	  \draw [<-] (input-\i) -- ++(-1,0)
	    node [above, midway] {$I_\l$};

	% hidden layer
	\foreach \l [count=\i] in {1,2}
	  \node [above] at (hidden-\i.north) {$H_\l$};

	% output neurons
	\foreach \l [count=\i] in {1}
	  \draw [->] (output-\i) -- ++(1,0)
	    node [above, midway] {$O_\l$};

	% input -> hidden
	\foreach \i in {1,...,4}
	  \foreach \j in {1,...,2}
	    \draw [->] (input-\i) -- (hidden-\j);

	% hidden -> output
	\foreach \i in {1,...,2}
	  \foreach \j in {1}
	    \draw [->] (hidden-\i) -- (output-\j);

	% labels above layers
	\foreach \l [count=\x from 0] in {Input, Hidden, Ouput}
	  \node [align=center, above] at (\x*2,2) {\l \\ layer};

	\end{tikzpicture}
\caption{Neural Network example}
\label{neural_network}
\end{figure}
